Supporting Information: The Transport Mechanisms of Polar Solutes in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane

### 2019-03-25 Ben_Manuscripts/transport/Supporting_Information.tex
Figure and organization updates

  \subsection{Hydrogen Bond Detection Sensitivity}\label{section:hbond_sensisitivity}

@@

>>>>

  \subsection{Hydrogen Bond Detection Sensitivity}\label{section:hbond_sensitivity}

@@

  \subsection{Solute Pairing with Sodium}

  \begin{figure}[!htb]
  \centering
  %MRS2: would be better if this was paired with ensemble data, instead of just one trajectory.
  \includegraphics[width=0.45\textwidth]{na_met_trace.pdf}  % create with nn.py located in MET/10wt
  \caption{The oxygen atom of methanol stays within 2.5 \AA~of the same sodium ion for
  the majority of the trapping occurence between 400 and 600 ns. Regions
  highlighted red or blue indicate times when methanol's oxygen atom is within 
  2.5 \AA~of a sodium ion. The color of the shaded regions are switched every time
  the oxygen atom becomes associated to a different sodium ion.}\label{fig:na_met_trace}
  \end{figure}

  %BJC: could probably safely remove this figure
  \subsection{Mercaptoethanol's range of behavior}

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\linewidth]{SOH_trace.pdf}
  \caption{}\label{fig:SOH_trace}
  \end{subfigure}
  \caption{Mercaptoethanol exhibits transport behavior ranging from frequent hopping
  to lengthy trapping. Large hops generally occur near the pore center while 
  long entrapments occur while tangled among the monomer tails.}
  \end{figure}

  \subsection{THF-sodium Complexation}

  \begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{thf_sodium_coordination.pdf}
  \caption{Coordination of THF with sodium ions may help stabilize it inside the
  pore region. For the first 700 ns of the trajectories shown, the center of mass
  of THF (top line in top figure) and a sodium ion (bottom line in top figure) move
  in tandem. The distance between the oxygen atom of THF and the sodium ion has only
  occasional fluctuations away from a relatively stable separation of ca. 0.25 nm. 
  After 700 ns, THF separates from the sodium ion and moves closer to the head group
  region.}\label{fig:thf_sodium_coordination}
  \end{figure}
  %MRS2: Can we show something that describes a distribution of multiple THF? this is just one, 
  % which is suggestive, but this sort of suggestive information maybe should be in supporting. 
  %MRS2: did you trace down any information on THF-ion complexation? We should be able to report on whether
  %this is physical or a force field artifact.
  % BJC2: probably better to find evidence of ether-ion complexation since it applies to multiple
  % solutes that we studied
